Supplemental Materials

### 2021-06-22 supplement/supplement-main.Rmd
minor supplement edits
fixing cog model running

$$\mu = \exp\Bigg(\ln\Big(1 - \exp\big(\ln\big(1-w_0) + \sum_i(1-w_i)x_i\big)\big) \Big) + \ln\Big(\sum_i(1-w_i)(1-x_i)\Big)\Bigg)$$

$$y \sim beta\big(\mu k, (1-\mu)k\big)$$

@@

## uncomment to re-run cross validation
# source("../code/custom-structure-learning/fit-cog-models-bnlearn.R")

@@

```{r, echo=F}
## examine bootstrapping results

@@

## what is strength of each arc in final graph?
bnlearn_to_df(main_model) %>% 
  left_join(boot_res, by=c("from","to"))  %>% 
  filter(strength > .80)
```

@@

$$logit(\mu) = logit(pretest) + \ln(ER_0) + x\ln(ER_{1})$$

$$y \sim beta\big(\mu k, (1-\mu)k\big)$$

@@

$$ p(evidence = 1 | x ) = .50*ER_1$$

$$ p(evidence = 0 | x) = .50. $$

>>>>

$$y \sim beta\big(\mu k, (1-\mu)k\big)$$
$$\mu = \exp\Bigg(\ln\Big(1 - \exp\big(\ln\big(1-w_0) + \sum_i(1-w_i)x_i\big)\big) \Big) + \ln\Big(\sum_i(1-w_i)(1-x_i)\Big)\Bigg)$$

@@

if (!file.exists("../local/cv-res.rds")){
  source("../code/custom-structure-learning/fit-cog-models-bnlearn.R", chdir=TRUE)
}

@@

```{r, echo=F, include=F}
## examine bootstrapping results

@@

## what is strength of each arc in final graph?
bnlearn_to_df(main_model) %>% 
  left_join(boot_res, by=c("from","to"))  %>% 
  filter(strength > .95)
```

@@

$$y \sim beta\big(\mu k, (1-\mu)k\big)$$
$$logit(\mu) = logit(pretest) + \ln(ER_0) + x\ln(ER_{1})$$

@@

$$ p(evidence = 1 | x ) = .50*ER_1$$ 
$$ p(evidence = 0 | x) = .50. $$
